lfl: An \R{} Package for Linguistic Fuzzy Logic

### 2021-06-10 article.tex
Updates from Overleaf

In \pkg{arules}, the process is as follows. First of all, the numeric data have to be transformed into categories. The standard \R{}'s \texttt{cut()} function can be used for that. The following command transforms the numeric variables into five equidistant interval categories:
%
\input{chunks/chunk-casestudy-assoc-arules}
%

>>>>

In \pkg{arules}, the process is as follows. First of all, the numeric data have to be transformed into categories. The standard \R{}'s \texttt{cut()} function can be used for that. The following command transforms the numeric variables into five equidistant interval categories:
%
\input{chunks/chunk-casestudy-assoc-arules}
%
Now the data may be transformed into transactions and the rules may be searched with antecedents, consequents, minimum support and confidence set as above:
%
\input{chunks/chunk-casestudy-assoc-arules-search}
%
The \pkg{arules} package has found 64 rules, from which the 8 rules with the greatest confidence are as follows:
%
\input{chunks/chunk-casestudy-assoc-arules-view}
%
